Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-07 nlp.tex
Some more points and outline to fill out

Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolve to. For example, in a date string 5/6/2015, the pattern could either be M/d/yyyy or d/M/yyyy.

>>>>

While there are several functionally equivalent notations for representing CFG, we use the \textit{Backus-Naur Form} (BNF) for defining the grammar rules for \texttt{DATEPARSE} formats.

%
%   date-fullyear   = 4DIGIT
%   date-month      = 2DIGIT  ; 01-12
%   date-mday       = 2DIGIT  ; 01-28, 01-29, 01-30, 01-31 based on month/year
%   time-hour       = 2DIGIT  ; 00-23
%   time-minute     = 2DIGIT  ; 00-59
%   time-second     = 2DIGIT  ; 00-58, 00-59, 00-60 based on leap second
%                             ; rules
%   time-secfrac    = "." 1*DIGIT
%   time-numoffset  = ("+" / "-") time-hour ":" time-minute
%   time-offset     = "Z" / time-numoffset
%
%   partial-time    = time-hour ":" time-minute ":" time-second
%                     [time-secfrac]
%   full-date       = date-fullyear "-" date-month "-" date-mday
%   full-time       = partial-time time-offset
%
%   date-time       = full-date | full-time

\subsection{Production Rule Constraints}

\subsection{Probabilistic Context-Free Grammar}
Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolve to. For example, in a date string 5/6/2015, the pattern could either be M/d/yyyy or d/M/yyyy.
